---
title: "My project"
author: "Rainbow"
date: "2024-10-11"
output: "github_document"
---



```{r}
library(haven)
library(dplyr)
library(tidyr)
library(ggplot2)
library(psych)
library(bruceR)
library(ggsci)
library(see)
library(car)
library(Rmisc)
library(rstatix)
library(emmeans)
library(labelled)
library(ggstatsplot)
library(performance)
library(sjPlot)

dataset <- read.csv("/Users/rainbow/Documents/project\ dataset.csv")

```

#Recode variables
```{r}
dataset <- dataset %>%
  mutate_at(c('gender'),funs(str_replace(., "1", "Men")))

dataset <- dataset %>%
  mutate_at(c('gender'),funs(str_replace(., "2", "Women")))
```

#Regression (SE, power, authenticity)
##Correlation
```{r}
regression <- dataset %>%
  select(power, authenticity, Self_esteem, relationship_satis)

Corr(regression)
```
##Regression
```{r}
model<-lm(relationship_satis ~ power + authenticity + Self_esteem, data = regression)

check_model(model)

model_summary(model)

tab_model(model)

plot_model(model,  type ="est",  show.values = TRUE, vline.color = "#1B191999", line.size = 1.5, dot.size = 2.5, colors = "#276bbd") + theme_bruce() +
  labs(
    title = "Relationship Satisfaction",
  )


```
# Regression (SE and gender)
## Correlation
```{r}
dataset <- dataset %>%
  mutate_at(c('gender'),funs(str_replace(., "Men", "1")))

dataset <- dataset %>%
  mutate_at(c('gender'),funs(str_replace(., "Women", "2")))

regression2 <- dataset %>%
  select(gender, Self_esteem, relationship_satis)

Corr(regression2)

```
## Regression
```{r}
model<-lm(relationship_satis ~ Self_esteem * gender, data = regression2)

check_model(model)

model_summary(model)

tab_model(model)

plot_model(
  model,
  type = "est",
  show.values = TRUE,
  vline.color = "#1B191999",
  line.size = 1.5,
  dot.size = 2.5,
  colors = "#276bbd",
  axis.labels = c("Self esteem x Gender", "Gender", "Self esteem")
) +
  theme_bruce() +
  labs(
    title = "Relationship Satisfaction"
  )
    
```

# Reliability for self-esteem
```{r}
Alpha(dataset, "se", 1:10)
```

# Reliability for relationship satisfaction
```{r}
colnames(dataset)[colnames(dataset) == "Relationship1"] <- "R1"

Alpha(dataset, "R", 1:7)
```

# Exploratory Factor Analysis for Self-esteem
```{r}
EFA(dataset, "se", 1:10, method = "pa", plot.scree = TRUE, nfactors = c("parallel"))
```

# Exploratory Factor Analysis for relationship satisfaction
```{r}
EFA(dataset, "R", 1:7, method = "pa", plot.scree = TRUE, nfactors = c("parallel"))
```
# Reliability for power and authenticity
## Rename columns 
```{r}
colnames(dataset)[colnames(dataset) == "Power1"] <- "P1"
colnames(dataset)[colnames(dataset) == "A_Living1"] <- "A1"
colnames(dataset)[colnames(dataset) == "A_Living2"] <- "A2"
colnames(dataset)[colnames(dataset) == "A_Living3"] <- "A3"
colnames(dataset)[colnames(dataset) == "A_L4"] <- "A4"
colnames(dataset)[colnames(dataset) == "A_aliennation1"] <- "A5"
colnames(dataset)[colnames(dataset) == "A_a2"] <- "A6"
colnames(dataset)[colnames(dataset) == "A_a3"] <- "A7"
colnames(dataset)[colnames(dataset) == "A_a4"] <- "A8"
colnames(dataset)[colnames(dataset) == "A_other1"] <- "A9"
colnames(dataset)[colnames(dataset) == "A_o2"] <- "A10"
colnames(dataset)[colnames(dataset) == "A_o3"] <- "A11"
colnames(dataset)[colnames(dataset) == "A_o4"] <- "A12"

```

## Reliability of power 
```{r}
Alpha(dataset, "P", 1:8)
```

## Reliaibility of authenticity
```{r}
Alpha(dataset, "A", 1:4)
Alpha(dataset, "A", 5:8)
Alpha(dataset, "A", 9:12)

Alpha(dataset, "A", 1:12)
```

## Factor analysis for power 
```{r}
EFA(dataset, "P", 1:8, method = "pa", plot.scree = TRUE, nfactors = 1)
```
## Factor analysis for authenticity
```{r}
EFA(dataset, "A", 1:4, method = "pa", plot.scree = TRUE, nfactors = c("parallel"))
EFA(dataset, "A", 5:8, method = "pa", plot.scree = TRUE, nfactors = c("parallel"))
EFA(dataset, "A", 9:12, method = "pa", plot.scree = TRUE, nfactors = c("parallel"))
```

